---
title: "Explore dataset gapminder"
output: github_document
---
First, load the dataset.
```{r load, message=FALSE}
require(gapminder)
require(dplyr)
```
Take a glance at the head of the dataset.
```{r}
head(gapminder)
```
What is the size of the dataset?
```{r}
nrow(gapminder)
```
How many columns are there in this dataset?
```{r}
ncol(gapminder)
```
How about the last few rows of the datset?
```{r}
tail(gapminder)
```
What is the time-span of this dataset?
```{r}
range(gapminder$year)
```
How far can lifeExpectancy go?
```{r}
range(gapminder$gdpPercap)
```
What are the countries here?
```{r}
unique(gapminder$country)
```
What is the mean life expectancy in 1952?
```{r, message=FALSE, warning=FALSE}
mgapminder1952 = aggregate(na.omit(gapminder[gapminder$year==1952,]),
                           by=list(gapminder[gapminder$year==1952,]$continent),
                           FUN=mean)
mgapminder1952$country = NULL
mgapminder1952$continent = NULL
names(mgapminder1952)[1] = "continent"
mgapminder1952
```
How does it compare to now (2007)?
```{r, message=FALSE, warning=FALSE}
mgapminder2007 = aggregate(na.omit(gapminder[gapminder$year==2007,]), 
                           by=list(gapminder[gapminder$year==1952,]$continent), 
                           FUN=mean)
mgapminder2007$country = NULL
mgapminder2007$continent = NULL
names(mgapminder2007)[names(mgapminder2007) == "Group.1"] = "continent"
mgapminder2007
```
Life expectancy in all continents growed at different levels.
```{r}
dlgapminder = cbind(mgapminder2007["continent"],mgapminder2007["lifeExp"]-mgapminder1952["lifeExp"])
names(dlgapminder)[2] = "dLifeExp"
dlgapminder
```
